Type Refinements for the Working Class

### 2015-11-20 paper.tex
Make definition of approximation precise
This is, incidentally, a case where having that presheaf machinery would
have been very useful.

Now, we can extend $R_\tau$ to a new relation $[R_\tau]$ on closed expressions
which respects a single ``layer'' of computation, defined pointwise in the following way:
\begin{gather*}
  \infer{
    \SBinRel{[R_\tau]}{\Upsilon}{M}{N}
  }{
    \left(\Eval{\Upsilon}{\tau}{N}{\App{\vartheta}{\Vec{F}}}
    \quad
    \SBinRel{R_{\vec{v}}}{\Upsilon}{\vec{E}}{\vec{F}}\right)
    \quad
    \text{supposing}
    \quad
    \left(
      \Eval{\Upsilon}{\tau}{M}{\App{\vartheta}{\Vec{E}}},
      \Lookup{\CanOperators}{\vartheta}{\MkArity{\vec{v}}{\tau}}
    \right)
  }
\end{gather*}

>>>>

Now, we can extend $R_\tau$ to a new relation $[R_\tau]$ on closed expressions
which respects a single ``layer'' of computation. We will say
$\SBinRel{[R_\tau]}{\Upsilon}{M}{N}$ when, supposing
$\Eval{\Upsilon}{\tau}{M}{\App{\vartheta}{\Vec{E}}}$ such that
$\Lookup{\CanOperators}{\vartheta}{\MkArity{\vec{v}}{\tau}}$, for any
$\Of{\rho}{\Upsilon\inj\Upsilon'}$, we have
$\Eval{\Upsilon'}{\tau}{N\rho}{\App{\vartheta\rho}{\Vec{F}\rho}}$ and
$\SBinRel{R_{\vec{v}}}{\Upsilon'}{\vec{E}\rho}{\vec{F}\rho}$.
